Manuscript drafts

### 2020-03-09 manuscript/drafts/manuscript.Rmd
Dataset preprocessing - updated noteobook on preprocessing for 4/5 datasets - updated meeting notes - renamed meeting notes

---
title: "Manuscript drafts"
author: "Gerbrich Ferdinands"
date: "1/14/2020"
output: pdf_document
bibliography: asreview.bib
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(knitr)
library(xtable)
library(kableExtra)
library(captioner)
library(glue)

@@

```{r all tables, results = 'hide'}
table_nums <- captioner(prefix = "Table")
table_nums(name = "datasets", caption = "Descriptive statistics on articles and resulting datasets for each original systematic review.")
```

@@

@@

## Background
[@Yu2018a, @Yu2019] simulated 32 svm classifiers, on software engineering.

In terms of Yu et al, we adopt .CT.

@@

## Datasets
The algorithm will be tested on five systematic reviews from various research areas. 
test datasets serve as systematic search results, then perform active learning to detect inclusions.

#### ace
The ACEInhibitors dataset from the study by [@Cohen2006].
The study includes several data sets from the medical sciences, one of them is on ACE inhibitors.

@@

- systematic search n = 3453
- full text screening n = 174
- included in synthesis n = 26

... dataset is ...

Descriptive statistics on the reviews can be found in `r table_nums("datasets", display = "cite")`. 
All datasets accompanying the systematic reviews are openly published. 
The datasets contain information on all citations obtained in the search strategy and which citations were included in the systematic review.

@@

Entries with missing abstracts were removed. 
Duplicate entries were removed. 
Preprocessing scripts can be found on the GitHub repository

@@

tibble(Dataset = names(all), 
       #Citation = NA, # maybe add footnote citation with kableExtra i.o. this.
       `No. studies` = sapply(all, function(x) x[1,1]), 
       `No. selected for fulltext screening` = sapply(all, function(x) x[1,2]),
       `No. final inclusions` = sapply(all, function(x) x[1,3]),
       `Inclusion rate (%)` = sapply(all, function(x) round(x[1,3]/x[1,1]*100,2)),
       `No. studies in test collection` = sapply(all, function(x) x[3,1]),
       `No. selected for fulltext screening test collection` = sapply(all, function(x) x[3,2]),
       `No. final inclusions in test collection` = sapply(all, function(x) x[3,3]),
       `Inclusion rate in test collection (%)` = sapply(all, function(x) round(x[3,3]/x[3,1]*100,2))
       ) %>%
  # knitr kable
  kable(format = "latex",
        booktabs = TRUE,
        caption = table_nums("datasets")) %>%
  kable_styling(full_width = TRUE) %>%
  add_header_above(c("", "Original study" = 4, "Test collection" = 4))

  # add citations
```

@@

@@

A simulation is of one model on one dataset. 
we have a model $M$ using a classifier $c$ with (hyper)parameters $h$, performing an automated systematic review on SR dataset $d$. 
The model starts with 5 inclusions and 5 exclusions, randomly selected. The simulation is repeated for 10 trials $t$. 
We use 5 inclusions and exclusions as we assume the researcher has some prior knowledge on this. 
for every for every model (5), for every dataset (5) and for every set of optimized hyperparameters (3), a simulation study consisting trials is performed. From these $5*5*3=75$ simulation studies, performance of the different models is evaluated.

@@

 - decisions of the original SR are **ground truth** (benchmark) (oracle)

 - binary classifications: relevant/irrelevant

@@

### Stage 1: hyperparameter optimization
We are going to test 5 models on 5 different datasets.

### Models
- Naive Bayes 
- Random Forests
- Support Vecor Machine 
- Logistic Regression
- Dense Neural Network

@@

The other parameters remain fixed over the 5 models:

>>>>

---
title: "Manuscript drafts"
author: "Gerbrich Ferdinands"
date: "1/14/2020"
output: 
  pdf_document:
    citation_package: biblatex
bibliography: asreview.bib

---
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(knitr)
library(xtable)
library(kableExtra)
library(captioner)
library(glue)
library(rbbt)

@@

```{r all tables, results = 'hide'}
table_nums <- captioner(prefix = "Table")
# table  on datasets statistics
table_nums(name = "datasets", caption = "Statistics on datasets from original systematic reviews.")
```

@@

RQ1

@@

- pool unlabeled abstracts $\mathcal{U}$ 
- labeled data set $\mathcal{L}$, 
- instance $x$, label $y$

- utility measure $\phi_A(\cdot)$
- $x^*_A$ best query instance according to $\phi_A(\cdot)$

```{}
while

## Background
[@Yu2018a], [@Yu2019] simulated 32 svm classifiers, on software engineering. 
A popular classifier is SVM 
In terms of Yu et al, we adopt .CT.

@@

## Datasets

The algorithm will be tested on five systematic reviews from various research areas. 
test datasets serve as systematic search results, then perform active learning to detect inclusions.

#### ace 
A dataset from a collection of systematic reviews on drug efficacy from the medical sciences [@Cohen2006]. 
This dataset is on a systematic review

efficacy of Angiotensin-converting enzyme (ACE) inhibitors.
The ace dataset comes from a study on reducing workload in systematic reviews  [@Cohen2006].
The ace dataset is on the efficacy of

drug class 
The ACEInhibitors dataset from the study by [@Cohen2006].
The study includes several data sets from the medical sciences, one of them is on ACE inhibitors.

@@

Statistics on the SRs can be found in `r table_nums("datasets", display = "cite")`. 
All datasets accompanying the systematic reviews are openly published. 
The datasets contain information on all citations obtained in the search strategy and which citations were included in the systematic review.

@@

Entries with missing abstracts were removed. 
Duplicate entries were removed. 
Preprocessing scripts can be found on the GitHub^[https://github.com/GerbrichFerdinands/asreview-thesis]

@@

nstudies <- function(all, datastage, col){
}

nostudies <- function(all, set, stage){
  sapply(all, function(x) x[set, stage])
}
inclrate <- function(all, set){
  sapply(all, function(x) round(x[set,"incl"]/x[set,"search"]*100,2))
}

datastats <- 
  tibble(Dataset = names(all), 
       #Citation = NA, # maybe add footnote citation with kableExtra i.o. this.
       # paper 
       `candidates_paper` = nostudies(all, "paper", "search"), 
       #`fulltext_paper` = nostudies(all, "paper", "ftext"),
       `incl_paper` = nostudies(all, "paper", "incl"),
       `inclrate_paper` = inclrate(all, "paper"),
       # test set 
       `candidates_test` =  nostudies(all, "test", "search"), 
       #`fulltext_test` =  nostudies(all, "test", "ftext"), 
       `incl_test` =  nostudies(all, "test", "incl"), 
       `inclrate_test` = inclrate(all, "test")
       ) 
```

`r table_nums("datasets")`
```{r}
datastats %>%
  kable(format = "latex",
        booktabs = TRUE,
        col.names = c("Dataset", rep(c("Candidate studies", 
                                       #"Studies selected for fulltext screening", 
                                       "Final inclusions", 
                                       "Inclusion rate (%)"),2))) %>%
  kable_styling(full_width = TRUE) %>%
  add_header_above(c("", "Original study" = 3, "Test collection" = 3))
```

@@

## Models 
Now, we build five different active learning models.

we have a model $M$ using a classifier $c$ with (hyper)parameters $h$, performing an automated systematic review on SR dataset $d$.

We are going to test 5 models on 5 different datasets.

classifier - feature extraction - query strategy - balance strategy

BTMD -

#### Classifiers
- Naive Bayes (B)
- Random Forests (R)
- Support Vecor Machine (S)
- Logistic Regression (L)
- Dense Neural Network (N)

#### Feature extraction strategies
To compute relevancy of a paper, we use the title and abstract 
- baseline model:

### Balance strategies
triple = 
The other parameters remain fixed over the 5 models:

@@

A simulation is of one model on one dataset.

The model starts with 5 inclusions and 5 exclusions, randomly selected. The simulation is repeated for 10 trials $t$. 
We use 5 inclusions and exclusions as we assume the researcher has some prior knowledge on this. 
The researcher has some prior knowledge about the pool, some papers ought to be included in the SR
for every for every model (5), for every dataset (5) and for every set of optimized hyperparameters (3), a simulation study consisting trials is performed. From these $5*5*3=75$ simulation studies, performance of the different models is evaluated.

@@

 - decisions of the original SR are **ground truth** (benchmark) (oracle)
 - binary classifications: relevant/irrelevant

@@

### Stage 1: hyperparameter optimization

@@
